Formalization of Forcing in Isabelle/ZF

### 2020-06-13 IJCAR2020/slides/forcing_IJCAR2020_slides.tex
I keep playing with the code review

\begin{frame}
  \frametitle{Paulson's \texttt{ZF-Constructible}}
  Let $C :: {}$ \isatt{i} $\Rightarrow$ \isatt{o} be a predicate on sets.
  \pause
  \begin{block}{Relativization of $\sbq$}
    $x \sbq^C y \equiv \forall z.\ C(z) \longrightarrow (z\in x
    \longrightarrow z\in y)$.
  \end{block}
  \pause
  \begin{block}{$\sbq$ is absolute}
    $\forall x\ y.\ C(x) \land C(y) \longrightarrow (x \sbq^C y
    \longleftrightarrow x\sbq y)$.
  \end{block}
  \pause 
  \texttt{ZF-Constructible} develops relativized version of the axioms
  and proves that many concepts are absolute for \textbf{transitive
    classes} $C$
  \[
  x\in y \land C(y)  \longrightarrow C(x).
  \]
  satisfying additional axioms.
\end{frame}

@@

\begin{frame}<1-12>[label=code-review]
  \begin{center}
    \only<01>{\includegraphics[scale=0.23]{kunen_powerset_01.png} \\ \includegraphics[scale=0.26]{isa_converted_01.png}}%
    \only<02>{\includegraphics[scale=0.23]{kunen_powerset_02.png} \\ \includegraphics[scale=0.26]{isa_converted_02.png}}%
    \only<03>{\includegraphics[scale=0.23]{kunen_powerset_03.png} \\ \includegraphics[scale=0.26]{isa_converted_03.png}}%
    \only<04>{\includegraphics[scale=0.23]{kunen_powerset_04.png} \\ \includegraphics[scale=0.26]{isa_converted_04.png}}%
    \only<05>{\includegraphics[scale=0.23]{kunen_powerset_05.png} \\ \includegraphics[scale=0.26]{isa_converted_05.png}}%
    \only<06>{\includegraphics[scale=0.23]{kunen_powerset_06.png} \\ \includegraphics[scale=0.26]{isa_converted_06.png}}%
    \only<07>{\includegraphics[scale=0.23]{kunen_powerset_07.png} \\ \includegraphics[scale=0.26]{isa_converted_07.png}}%
    \only<08>{\includegraphics[scale=0.23]{kunen_powerset_08.png} \\ \includegraphics[scale=0.26]{isa_converted_08.png}}%
    \only<09>{\includegraphics[scale=0.23]{kunen_powerset_09.png} \\ \includegraphics[scale=0.26]{isa_converted_09.png}}%
    \only<10>{\includegraphics[scale=0.23]{kunen_powerset_10.png} \\ \includegraphics[scale=0.26]{isa_converted_10.png}}%
    \only<11>{\includegraphics[scale=0.23]{kunen_powerset_11.png} \\ \includegraphics[scale=0.26]{isa_converted_11.png}}%
    \only<12>{\includegraphics[scale=0.23]{kunen_powerset_12.png} \\ \includegraphics[scale=0.26]{isa_converted_12.png}}%
    \only<13>{\includegraphics[scale=0.23]{kunen_powerset_13.png} \\ \includegraphics[scale=0.26]{isa_converted_13.png}}%
    \only<14>{\includegraphics[scale=0.23]{kunen_powerset_14.png} \\ \includegraphics[scale=0.26]{isa_converted_14.png}}%
    \only<15>{\includegraphics[scale=0.23]{kunen_powerset_15.png} \\ \includegraphics[scale=0.26]{isa_converted_15.png}}%
    \only<16>{\includegraphics[scale=0.23]{kunen_powerset_16.png} \\ \includegraphics[scale=0.26]{isa_converted_16.png}}%
    \only<17>{\includegraphics[scale=0.23]{kunen_powerset_17.png} \\ \includegraphics[scale=0.26]{isa_converted_17.png}}%
    \only<18>{\includegraphics[scale=0.23]{kunen_powerset_18.png} \\ \includegraphics[scale=0.26]{isa_converted_18.png}}%
    \only<19>{\includegraphics[scale=0.23]{kunen_powerset_19.png} \\ \includegraphics[scale=0.26]{isa_converted_19.png}}%
    \only<20>{\includegraphics[scale=0.23]{kunen_powerset_20.png} \\ \includegraphics[scale=0.26]{isa_converted_20.png}}%
  \end{center}
\end{frame}

>>>>

\begin{frame}
  \frametitle{\texttt{ZF-Constructible} \citep{paulson_2003}}
  Let $C :: {}$ \isatt{i} $\Rightarrow$ \isatt{o} be a predicate on sets.
  \pause
  \begin{block}{Relativization of $\sbq$}
    $x \sbq^C y \equiv \forall z.\ C(z) \longrightarrow (z\in x
    \longrightarrow z\in y)$.
  \end{block}
  \pause
  \begin{block}{$\sbq$ is absolute}
    $\forall x\ y.\ C(x) \land C(y) \longrightarrow (x \sbq^C y
    \longleftrightarrow x\sbq y)$.
  \end{block}
  \pause 
  \texttt{ZF-Constructible} develops relativized version of the axioms
  and proves that many concepts are absolute for \textbf{transitive
    classes} $C$
  \[
  x\in y \land C(y)  \longrightarrow C(x).
  \]
  satisfying additional axioms.
\end{frame}

@@

\begin{frame}<1-12>[label=code-review]
  \begin{center}\setlength{\fboxsep}{0pt}
    \only<01>{\includegraphics[scale=0.23]{kunen_powerset_01.png} \\ \fbox{\includegraphics[scale=0.26]{isa_converted_01.png}}}%
    \only<02>{\includegraphics[scale=0.23]{kunen_powerset_02.png} \\ \fbox{\includegraphics[scale=0.26]{isa_converted_02.png}}}%
    \only<03>{\includegraphics[scale=0.23]{kunen_powerset_03.png} \\ \fbox{\includegraphics[scale=0.26]{isa_converted_03.png}}}%
    \only<04>{\includegraphics[scale=0.23]{kunen_powerset_04.png} \\ \fbox{\includegraphics[scale=0.26]{isa_converted_04.png}}}%
    \only<05>{\includegraphics[scale=0.23]{kunen_powerset_05.png} \\ \fbox{\includegraphics[scale=0.26]{isa_converted_05.png}}}%
    \only<06>{\includegraphics[scale=0.23]{kunen_powerset_06.png} \\ \fbox{\includegraphics[scale=0.26]{isa_converted_06.png}}}%
    \only<07>{\includegraphics[scale=0.23]{kunen_powerset_07.png} \\ \fbox{\includegraphics[scale=0.26]{isa_converted_07.png}}}%
    \vspace{3.00115pt}\only<08>{\includegraphics[scale=0.23]{kunen_powerset_08.png} \\ \fbox{\includegraphics[scale=0.26]{isa_converted_08.png}}}%
    \only<09>{\includegraphics[scale=0.23]{kunen_powerset_09.png} \\ \fbox{\includegraphics[scale=0.26]{isa_converted_09.png}}}%
    \only<10>{\includegraphics[scale=0.23]{kunen_powerset_10.png} \\ \fbox{\includegraphics[scale=0.26]{isa_converted_10.png}}}%
    \only<11>{\includegraphics[scale=0.23]{kunen_powerset_11.png} \\ \fbox{\includegraphics[scale=0.26]{isa_converted_11.png}}}%
    \only<12>{\includegraphics[scale=0.23]{kunen_powerset_12.png} \\ \fbox{\includegraphics[scale=0.26]{isa_converted_12.png}}}%
    \only<13>{\includegraphics[scale=0.23]{kunen_powerset_13.png} \\ \fbox{\includegraphics[scale=0.26]{isa_converted_13.png}}}%
    \only<14>{\includegraphics[scale=0.23]{kunen_powerset_14.png} \\ \fbox{\includegraphics[scale=0.26]{isa_converted_14.png}}}%
    \only<15>{\includegraphics[scale=0.23]{kunen_powerset_15.png} \\ \fbox{\includegraphics[scale=0.26]{isa_converted_15.png}}}%
    \only<16>{\includegraphics[scale=0.23]{kunen_powerset_16.png} \\ \fbox{\includegraphics[scale=0.26]{isa_converted_16.png}}}%
    \only<17>{\includegraphics[scale=0.23]{kunen_powerset_17.png} \\ \fbox{\includegraphics[scale=0.26]{isa_converted_17.png}}}%
    \only<18>{\includegraphics[scale=0.23]{kunen_powerset_18.png} \\ \fbox{\includegraphics[scale=0.26]{isa_converted_18.png}}}%
    \only<19>{\includegraphics[scale=0.23]{kunen_powerset_19.png} \\ \fbox{\includegraphics[scale=0.26]{isa_converted_19.png}}}%
    \only<20>{\includegraphics[scale=0.23]{kunen_powerset_20.png} \\ \fbox{\includegraphics[scale=0.26]{isa_converted_20.png}}}%
  \end{center}
\end{frame}
